Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
Phrasing.

\noindent {\bfseries List of Tasks} 
The lists of tasks were originally inspired by the top Alexa sites, which gave an idea of relevant and popular browsing behavior, then refined by ethical concerns, filtering out tasks which would require a participant to reveal private information. The resulting task list is one which we hope is both representative of how a user might browse the internet, but also give good coverage of sites which are censored today.

>>>>

\noindent {\bfseries List of Tasks} 
The lists of tasks were originally inspired by the top Alexa sites, which gave an idea of relevant and popular browsing behavior, then refined by ethical concerns, filtering out tasks which would require a participant to reveal private information. The resulting task list is one which we hope is both representative of how a user might browse the internet, and also gives good coverage of sites which are censored today.
